### 2012-10-17 doc/ops/report.tex
first draft of project description

In academic research, there are a huge abundance of scientific papers available for
consumption for any given scientific pursuit. In 2010, the famous journal,
PLOS One (\url{http://plosone.org}), reached the 10,000 papers published milestone \cite{PlosOne2010}. If you 
are doing background reading for a paper you are authoring, or looking for 
research on a specific topic that interests you, the vast quantity of data available can often be
quite daunting and choosing which papers to read very difficult. This problem
is further exacerbated when there is a time limit on the research to be carried
out. Partridge aims to aid the reader in finding documents relative to their
interests through the use of Artificial Intelligence techniques.

>>>>

In academic research, there are a huge abundance of scientific papers available for
consumption for any given scientific pursuit. There are hundreds of journals,
each with thousands of articles published on a yearly basis. In 2010, the famous journal,
PLOS One (\url{http://plosone.org}), reached the 10,000 papers published
milestone \cite{PlosOne2010}. With the advent of internet publishing,
researchers have access to an immense volume of information at their disposal.

For researchers doing background reading for a paper they are authoring, or looking for 
research on a specific topic that interests them, the vast quantity of data available can often be
quite daunting and choosing which papers to read very difficult. This problem
is further exacerbated when there is a time limit on the research to be carried
out. Partridge aims to aid the reader in finding documents relative to their
interests through the use of Artificial Intelligence techniques.

The project will use a web interface to allow a user to indicate which
specific scientific fields they are interested in - either through manual entry
of interests and types of report or by allowing the application to collect a
list of papers that the user has already read and to learn their user profile.
The program will then suggest sets of papers from the corpus depending on their
contents and relevance to the user.
